---
title: "protocol_getting_and processing_stops_data"
author: "Malgorzata Olesiewicz"
date: "28 December 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(revgeo)
library(dplyr)
```

## Getting the Public Transportation Stops Data

The public tranbsportation data has been acessed from Berlin Open Data Portal under <https://daten.berlin.de/datensaetze/vbb-fahrplandaten-gtfs> on the 28th of December 2018. 
From the downloaded data the data set of *stops* have been chosen. The following document is a protocol of the conducted data processing 

The *stops* data set contains a list of all the public transportation stops in Berlin together with their geografical coordinates. As we are intrested in finding out how many stops are in each district following steps of data: 
*1. Loading data & removing not needed varaibles*
```{r, echo=TRUE}
stops=read.table("stops.txt", header = TRUE, sep = ",")
stops.data=stops%>% select(-c(stop_code, stop_desc, location_type, parent_station)) ### removing not needed columns
```
*2. Obtaining saving as new variable the postcode from longitude and latitude of each bus stop* 

```{r, echo= TRUE }
getting_zip= function(x,y){ ### writting function to obtain zip codes for every bus stop:lontitude and latitude as asrugments
zip=c()  ### creating an empty vector to store the results
for(i in 1:length(stops.data$stop_lon)){  ### loop to run the function for every observation
each_zip= revgeo(x[i], y[i], provider = NULL , output = 'frame', API = NULL, item = 'zip') ## using revgeo package to get zip code for every stop (open street maps as the default option)
zip=c(zip,each_zip[5])} ##saving the 5th elemnt (zip) for every observation and adding it to previouse zips
return(zip) ## returning the obtained data
}
zips=(matrix(unlist(getting_zip(stops.data$stop_lon,stops.data$stop_lat)))) ## running the function and converting the obtained level data into factor type

zip.code=c(as.character(zips)) ## converting factor type data into character (numeric not possible as some post codes start from 0) and saving it as a vector

stops.data$zip=zip.code ## adding the data to the data set

### THIS OPERATION TAKES VERY LONG TIME

write.csv(stops.data, "stops+zip2.csv")
```

*3. Obtaining and saving as new variable the name of the district 