---
title: "maps"
author: "Aleksandra Kudaeva"
date: "20 Januar 2019"
output: pdf_document
---

One morning, when Gregor Samsa woke from troubled dreams, he found himself transformed in his bed into a horrible vermin. He lay on his armour-like back, and if he lifted his head a little he could see his brown belly, slightly domed and divided by arches into stiff sections. The bedding was hardly able to cover it and seemed ready to slide off any moment. His many legs, pitifully thin compared with the size of the rest of him, waved about helplessly as he looked. "What's happened to me?" he thought. It wasn't a dream. His room, a proper human room although a little too small, lay peacefully between its four familiar walls. A collection of textile samples lay spread out on the table - Samsa was a travelling salesman - and above it there hung a picture that he had recently cut out of an illustrated magazine and housed in a nice, gilded frame. It showed a lady fitted out with a fur hat and fur boa who sat upright, raising a heavy fur muff that covered the whole of her lower arm towards the viewer. Gregor then turned to look out the window at the dull weather. Drops 

```{r libraries}
#install and upload packages
packages<-c("ggplot2", "ggmap", "sp", "mapproj", "maps", "mapoland", "osmdata", "rgdal")

for (package in packages) {
  if(!require(package, character.only=TRUE)){install.packages(package, character.only=TRUE)}
  library(package, character.only=TRUE)
}

```

One morning, when Gregor Samsa woke from troubled dreams, he found himself transformed in his bed into a horrible vermin. He lay on his armour-like back, and if he lifted his head a little he could see his brown belly, slightly domed and divided by arches into stiff sections. The bedding was hardly able to cover it and seemed ready to slide off any moment. His many legs, pitifully thin compared with the size of the rest of him, waved about helplessly as he looked. "What's happened to me?" he thought. It wasn't a dream. His room, a proper human room although a little too small, lay peacefully between its four familiar walls. A collection of textile samples lay spread out on the table - Samsa was a travelling salesman - and above it there hung a picture that he had recently cut out of an illustrated magazine and housed in a nice, gilded frame. It showed a lady fitted out with a fur hat and fur boa who sat upright, raising a heavy fur muff that covered the whole of her lower arm towards the viewer. Gregor then turned to look out the window at the dull weather. Drops 

```{r berlin map}
#Get Berlin Boundaries from OSM data
ber<-getbb("berlin")

#automatic bbox cut some parts of berlin out, that is why I manually adjust x coordinate. Adjustments are defined manually.
ber_adj<-ber
ber_adj["x","min"]<-ber_adj["x","min"]-0.18
ber_adj["x","max"]<-ber_adj["x","max"]+0.22
ber_adj["y","min"]<-ber_adj["y","min"]-0.02

map <- get_stamenmap(ber_adj, maptype="toner-lite", zoom = 11)

```

Sources:
https://data.technologiestiftung-berlin.de/dataset/bezirksgrenzen

```{r districts}

test<-readOGR("~/SPL-Project/Dirstrict Data/bezirksgrenzen.kml")
Bezirk<-fortify(test)
Bezirk$District<-ifelse(Bezirk$id=="0", "Reinickendorf", 
                        ifelse(Bezirk$id=="1", "Charlottenburg-Wilmersdorf", 
                          ifelse(Bezirk$id=="10", "Friedrichshain-Kreuzberg", 
                            ifelse(Bezirk$id=="11", "Tempelhof-Schoneberg", 
                              ifelse(Bezirk$id=="2", "Treptow-Kopenick", 
                                ifelse(Bezirk$id=="3", "Pankow", 
                                  ifelse(Bezirk$id=="5", "Lichtenberg", 
                                    ifelse(Bezirk$id=="4", "Neukolln", 
                                      ifelse(Bezirk$id=="6", "Marzahn-Hellersdorf", 
                                        ifelse(Bezirk$id=="7", "Spandau", 
                                          ifelse(Bezirk$id=="8", "Steglitz-Zehlendorf", 
                                            ifelse(Bezirk$id=="9", "Mitte","NA"
                                            )
                                          )
                                        )
                                      )
                                    )
                                  )
                                )
                              )
                            )
                          )
                        )
)

#Merge data for each district with polygon data
Bezirk_m<-merge(Bezirk, Results, by.x="District", by.y="district", all=TRUE)
Berlin_r<-merge(Bezirk, Results_Rent, by.x="District", by.y="district", all.x=TRUE)


```

One morning, when Gregor Samsa woke from troubled dreams, he found himself transformed in his bed into a horrible vermin. He lay on his armour-like back, and if he lifted his head a little he could see his brown belly, slightly domed and divided by arches into stiff sections. The bedding was hardly able to cover it and seemed ready to slide off any moment. His many legs, pitifully thin compared with the size of the rest of him, waved about helplessly as he looked. "What's happened to me?" he thought. It wasn't a dream. His room, a proper human room although a little too small, lay peacefully between its four familiar walls. A collection of textile samples lay spread out on the table - Samsa was a travelling salesman - and above it there hung a picture that he had recently cut out of an illustrated magazine and housed in a nice, gilded frame. It showed a lady fitted out with a fur hat and fur boa who sat upright, raising a heavy fur muff that covered the whole of her lower arm towards the viewer. Gregor then turned to look out the window at the dull weather. Drops 

```{r map1}
p1 <- ggmap(map, extent = "normal", maprange = FALSE) +
  geom_polygon(data = Bezirk, aes(long, lat, group = group, fill=District),
               colour = "red", alpha = 0.2) +
  theme_bw() +
  coord_map(projection="mercator",
            xlim=c(attr(map, "bb")$ll.lon, attr(map, "bb")$ur.lon),
            ylim=c(attr(map, "bb")$ll.lat, attr(map, "bb")$ur.lat))

print(p1)

```

One morning, when Gregor Samsa woke from troubled dreams, he found himself transformed in his bed into a horrible vermin. He lay on his armour-like back, and if he lifted his head a little he could see his brown belly, slightly domed and divided by arches into stiff sections. The bedding was hardly able to cover it and seemed ready to slide off any moment. His many legs, pitifully thin compared with the size of the rest of him, waved about helplessly as he looked. "What's happened to me?" he thought. It wasn't a dream. His room, a proper human room although a little too small, lay peacefully between its four familiar walls. A collection of textile samples lay spread out on the table - Samsa was a travelling salesman - and above it there hung a picture that he had recently cut out of an illustrated magazine and housed in a nice, gilded frame. It showed a lady fitted out with a fur hat and fur boa who sat upright, raising a heavy fur muff that covered the whole of her lower arm towards the viewer. Gregor then turned to look out the window at the dull weather. Drops 

```{r map2}
p2 <- ggmap(map, extent = "normal", maprange = FALSE) +
  geom_polygon(data = Bezirk_m, aes(long, lat, group = group, fill=Bezirk_m$'Physical Index1'),
               colour = "red", alpha = 0.2) +
  theme_bw() +
  coord_map(projection="mercator",
            xlim=c(attr(map, "bb")$ll.lon, attr(map, "bb")$ur.lon),
            ylim=c(attr(map, "bb")$ll.lat, attr(map, "bb")$ur.lat))

print(p2)

```

One morning, when Gregor Samsa woke from troubled dreams, he found himself transformed in his bed into a horrible vermin. He lay on his armour-like back, and if he lifted his head a little he could see his brown belly, slightly domed and divided by arches into stiff sections. The bedding was hardly able to cover it and seemed ready to slide off any moment. His many legs, pitifully thin compared with the size of the rest of him, waved about helplessly as he looked. "What's happened to me?" he thought. It wasn't a dream. His room, a proper human room although a little too small, lay peacefully between its four familiar walls. A collection of textile samples lay spread out on the table - Samsa was a travelling salesman - and above it there hung a picture that he had recently cut out of an illustrated magazine and housed in a nice, gilded frame. It showed a lady fitted out with a fur hat and fur boa who sat upright, raising a heavy fur muff that covered the whole of her lower arm towards the viewer. Gregor then turned to look out the window at the dull weather. Drops 

```{r map3}
p3<-ggplot(Berlin_r, aes(long, lat, group=group))+geom_polygon(aes(fill=Total.Index.Score))+
  scale_fill_gradient(low = "darkblue", high = "white")
print(p3)
```

One morning, when Gregor Samsa woke from troubled dreams, he found himself transformed in his bed into a horrible vermin. He lay on his armour-like back, and if he lifted his head a little he could see his brown belly, slightly domed and divided by arches into stiff sections. The bedding was hardly able to cover it and seemed ready to slide off any moment. His many legs, pitifully thin compared with the size of the rest of him, waved about helplessly as he looked. "What's happened to me?" he thought. It wasn't a dream. His room, a proper human room although a little too small, lay peacefully between its four familiar walls. A collection of textile samples lay spread out on the table - Samsa was a travelling salesman - and above it there hung a picture that he had recently cut out of an illustrated magazine and housed in a nice, gilded frame. It showed a lady fitted out with a fur hat and fur boa who sat upright, raising a heavy fur muff that covered the whole of her lower arm towards the viewer. Gregor then turned to look out the window at the dull weather. Drops 

```{r map4}
p4<-ggplot(Berlin_r, aes(long, lat, group=group))+geom_polygon(aes(fill=mietepreise_arr..Mietpreis.in.Euro.pro.m².))+
  scale_fill_gradient(low = "lightgreen", high = "darkgreen")
print(p4)
```
