---
title: "Getting Mobility Data"
author: "Malgorzata Olesiewicz"
date: "16 December 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Source of data: Berliner Verkehr in Zahlen 2013

The project uses the report *Berliner Verkehr in Zahlen 2013* (the report) as the source of data regarding parking spaces. To read full report please visit: <https://www.berlin.de/senuvk/verkehr/politik_planung/zahlen_fakten/download/Mobilitaet_dt_komplett.pdf>

The report has been acessed on the 16th of December 2018

## Processing the data

As the mobility data is only avaiable as a part of the written report, this protocol documents how the data have been collected into the csv file *berliner_verkehr_zahlen_daten.csv*, which has been uploaded on the GitHub side of the project (https://github.com/Olesiewitch/SPL-Project/tree/master/data)


## Districts 

For the convenience of the data sets merging, the numeration and names of the districts of Berlin have been sources from the statistik-berlin-brandenburg-daten.csv . 
```{r, echo= TRUE}
a= c("01 Mitte", "02 Friedrichshain-Kreuzberg", "03 Pankow", "04 Charlottenburg-Wilmersdorf", "05 Spandau", "06 Steglitz-Zehlendorf", "07 Tempelhof-Schöneberg", "08 Neukolln", "09 Treptow-Köpenick", "10 Marzahn-Hellersdorf", "11 Lichtenberg", "12 Reinickendorf")
```

## Parking spaces 

The data regarding parking spaces in the districs of Berlin have been sourced from the page 32 of the report. Original name of data "Bewirtschaftete Stellplätze im öffentlichen  Straßenraum". 

```{r, echo=TRUE }
d=c(26488,4090,26000,20500,2726,7400,7150) ### avaiable data
b= c(26488,4090,26000,20500,2726,7400,7150,mean(d),mean(d),mean(d),mean(d),mean(d)) ## for the remaining districts taking the mean
```

## Mergin the data 

```{r, echo=TRUE}
berliner_verkehr_zahlen_daten = data.frame(a,b) 
```
## Colummn names
```{r pressure, echo=FALSE}
colnames(berliner_verkehr_zahlen_daten)=c("District","Parking Spaces")
```

## Writting .csv file 

```{r pressure, echo=FALSE}
write.csv(berliner_verkehr_zahlen_daten, "berliner_verkehr_zahlen_daten.csv")
```

