---
title: "Untitled"
author: "Wu Qi"
date: "1/13/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Getting the data 
The data has been obtaine from the Berlin Open Data Portal under the link <https://www.berlin.de/restaurants/stadtteile/>
The data has been downloaded as HTML file, and opened in Excel, the exact number of restaurant in districts has been exracted from the information opened in Excel with "countif" function one by one.The following protocol presents the process of writting the csv file.The written csv file has been stored on the Github page of the project under:  <https://github.com/Olesiewitch/SPL-Project/tree/master/Dirstrict%20Data>


```{r,include=TRUE}
library(readxl)
Nr_of_restaurant <- read_excel("Nr_of_restaurant.xlsx")
View(Nr_of_restaurant)
Nr_of_restaurant<-data.frame(Nr_of_restaurant$district[1:12],Nr_of_restaurant$X__3[1:12])

## Writting csv
write.csv(Nr_of_restaurant,"~/SPL-Project/Dirstrict Data/Nr_of_restaurant.csv")
```