---
title: "protocol- getting data - Kriminalitätsatlas Berlin"
author: "Malgorzata Olesiewicz"
date: "27 December 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Getting the data 

The data has been obtaine from the Berlin Open Data Portal and accessed on the 27th of December 2018 under the link <https://daten.berlin.de/datensaetze/kriminalit%C3%A4tsatlas-berlin> 
The data has been downloaded as excel spreedsheet. The chosen for the project criminal offences data has been written in R into a csv file. The following protocol presents the process of writting the csv file. The written csv file has been stored on the Github page of the project under:  <https://github.com/Olesiewitch/SPL-Project/tree/master/Dirstrict%20Data> 

### Crime frequancy
Excel sheet : HZ 2017 
Original name of data : Insgesamt-Straftaten (Häufigkeitszahlen (HZ) der Bezirke und Bezirksregionen)
English translation: Crime Frequancy
Year: 2017
Unit: Total number
```{r ,echo= TRUE}
crime =c(25864,19460,9718,15767,10888,7664,11385,12937,9239,9385,9663,11456)
districts= c("Mitte","Friedrichshain-Kreuzberg","Pankow","Charlottenburg-Wilmersdorf","Spandau", "Steglitz-Zehlendorf","Tempelhof-Schöneberg","Neukölln","Treptow-Köpenick","Marzahn-Hellersdorf", "Lichtenberg","Reinickendorf") 
criminal_offences = data.frame (districts, crime)
```

## Writting csv

```{r, echo= TRUE}
write.csv(criminal_offences, "kriminalitatsatlas_berlin_daten.csv")