---
title: "protocol- getting and merging data fbinter.stadt-berlin"
author: "Malgorzata Olesiewicz"
date: "26 December 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Getting Data 
The data has been obtained from the <http://www.stadtentwicklung.berlin.de//geoinformation/fis-broker/> website.The data has been acessed on the 26th of December. The developed by the city of Berlin data base does not allow for coping links to selected data sets. Therefore, detail instructions of how to look for specific data sets will be given for every data used. The chosen data has been stored in the excel spreedsheet on the GitHub page of the project under <https://github.com/Olesiewitch/SPL-Project/tree/master/Dirstrict%20Data>

### Street crossings
Name of the dataset:Fußgängerüberwege 
Search options: Archivsuche 
Original name: Fußgängerüberwege
English Translation: Street Crossing  

##Lenthg of cycling lines
Name of the dataset:Radverkehrsanlagen
English Translation: Lenthg of cycling lines 

## Colummn names
```{r pressure, echo=FALSE}
colnames(fbinter.stadt-berlin-daten)=c("Districts","Street_crossings","Lenthg_of_cycling_lines")
```

## Inserting the data
```{r ,echo= TRUE}
Street_crossings =c(33,39,54,35,22,31,19,25,32,39,22,30)
Lenthg_of_cycling_lines=c(169677.4,90134.7,161242.6,169577.9,165372.5,194599.2,148588.8,104444,202059.2,118019.1,100257,140794.4)
Districts= c("Mitte","Friedrichshain-Kreuzberg","Pankow","Charlottenburg-Wilmersdorf","Spandau", "Steglitz-Zehlendorf","Tempelhof-Schöneberg","Neukölln","Treptow-Köpenick","Marzahn-Hellersdorf", "Lichtenberg","Reinickendorf") 
data.frame (Districts, Street_crossings,Lenthg_of_cycling_lines)
```
