---
title: "protocol- getting and cleaning statistic data"
author: "Malgorzata Olesiewicz"
date: "16 December 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Source of data https://de.statista.com

The data from the <https://de.statista.com> portal have been acessed on the 20th of November 2018. The have been downloaded from the website and saved on the GitHub website of the project <https://github.com/Olesiewitch/SPL-Project/District-Data>. 

The following protocol documents how diffrent data sets have been merged together into one csv file *statista.csv*


## Districts 
The names of the districts have been keept in accordance to the portal standard. The order has been kep in occordance to *statistic_id652680_strassenbaeume-in-berlin-nach-bezirken-2017.xlsx* file.  

```{r, echo= TRUE}
library(readxl)
Trees = read_excel("statistic_id652680_strassenbaeume-in-berlin-nach-bezirken-2017.xlsx", 
sheet = "Daten")
```

```{r, echo=TRUE}
Districts = Trees[3:14,1] 
```

## Total Trees

Data obtained from 
<https://de.statista.com/statistik/daten/studie/652680/umfrage/strassenbaeume-in-berlin-nach-bezirken/> 
Original name: Absoluter Bestand
English Translation : Total trees
Unit: Total
Year:2017

```{r cars}
total_trees= Trees[3:14,2] 
```

## Trees per km

<https://de.statista.com/statistik/daten/studie/652680/umfrage/strassenbaeume-in-berlin-nach-bezirken/> 
Original name: Absoluter Bestand
English Translation : Total trees
Unit: Total
Year:2017

```{r cars}
trees_km= Trees[3:14,3] 
```

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
